Resource Buying Games

### 2017-03-01 paper.tex
game def

\section{Congestion Model}
In this section we want to introduce a structure to model resources and demands
of actors on resources. Therefore, we consider a set of players $N$ and a set
of resources $E$. Every player has a personal aim which can be achieved by
different resources. This is modelled for a player $i\in N$ as family
$\mathcal{S}_{i}$ of sets $S_{i}\subseteq E$ of resources. Additionally, we
want to account for different demands of players on resources by fixing a
demand for every player $i$ as $d_{i}\in\mathbb{N}$. Finally, the cost of a
resource depends on the load the players put onto the resource modelled as
individual cost functions $c_{e}:\mathbb{N}\rightarrow \mathbb{N}$ for every
resource $e\in E$. As an example consider different actors that build a shared
network infrastructure. The connections in the network are resources, the
actors are the players which have individual spots they want to connect.
Different actors might need different bandwidth for connections, i.e. their
demands, and the cost for using connections depends on the used bandwidth.
Accordingly we obtain a congestion model
\begin{equation*}
  \mathcal{M} = \tupel{N, E, \mathcal{S} = \times_{i\in N}\mathcal{S}_{i},
  (d_{i})_{i\in N}, (c_{e})_{e\in E}}
\end{equation*}
for which we introduce some additional definitions:
\begin{itemize}
  \item for a profile $S\in\mathcal{S}$ we define
    the demand on resource $e$ for $S$ as
    $\ell(S) = \sum_{i\in N:e\in S_{i}}d_{i}$
  \item we lift $c_{e}$ to the set $\mathcal{S}$ by setting
    $c_{e}(S) = c_{e}(\ell_{e}(S))$ for $S\in\mathcal{S}$
\end{itemize}
\todo{complete list of auxilary definitions}

\section{Matroids}
In this section we present the combinatorial structure of Matroids.
\todo{why matroids?}

>>>>

\section{Congestion Model}
In this section we want to introduce a structure to model resources and demands
of actors on resources. Therefore, we consider a set of players $N$ and a set
of resources $E$. Every player has a personal aim which can be achieved by
different resources. This is modelled for a player $i\in N$ as family
$\mathcal{S}_{i}$ of sets $S_{i}\subseteq E$ of resources. Additionally, we
want to account for different demands of players on resources by fixing a
demand for every player $i$ as $d_{i}\in\mathbb{N}$. Finally, the cost of a
resource depends on the load the players put onto the resource modelled as
individual cost functions $c_{e}:\mathbb{N}\rightarrow \mathbb{N}$ for every
resource $e\in E$. As an example consider different actors that build a shared
network infrastructure. The connections in the network are resources, the
actors are the players which have individual spots they want to connect.
Different actors might need different bandwidth for connections, i.e. their
demands, and the cost for using connections depends on the used bandwidth.
Accordingly we obtain a congestion model
\begin{equation*}
  \mathcal{M} = \tupel{N, E, \mathcal{S} = \times_{i\in N}\mathcal{S}_{i},
  (d_{i})_{i\in N}, (c_{e})_{e\in E}}
\end{equation*}
for which we introduce some additional definitions:
\begin{itemize}
  \item for a profile $S\in\mathcal{S}$ we define
    the demand on resource $e$ for $S$ as
    $\ell(S) = \sum_{i\in N:e\in S_{i}}d_{i}$
  \item we lift $c_{e}$ to the set $\mathcal{S}$ by setting
    $c_{e}(S) = c_{e}(\ell_{e}(S))$ for $S\in\mathcal{S}$
\end{itemize}

The cost that results from a profile $S\in\mathcal{S}$ is covered by all
players. To model this we consider the game 
\begin{equation*}
  G = \tupel{N, \mathcal{S}\times\mathcal{P}, \pi}
\end{equation*}
where $\mathcal{P} = \times_{i\in N}\mathcal{P}_{i}$ and
$\mathcal{P}_{i} = |\mathbb{R}_{+}^{|E|}|$ to model how much every player
contributes in paying for the cost of every resource. We denote the element
from $\mathcal{P}_{i}$ for $e\in E$ with $p_{i}^{e}$ and call $e\in E$ bought
under $\tupel{S, p}\in \mathcal{S}\times\mathcal{P}$ if
$c_{e}(S)\leq \sum_{i\in N}p_{i}^{e}$. The function $\pi$ gives the payoff for
every player for a strategy profile $\tupel{S, p}$ by
\begin{equation*}
  \pi_{i}(S, p) = \begin{cases}
    \sum_{e\in E}p_{i}^{e} &\text{ if $S_{i}$ is bought under
    $\tupel{S, p}$ (i.e. all $e\in S_{i}$ are bought)}\\
    \infty &\text{ otherwise}
  \end{cases}
\end{equation*}
Thus, every player tries to minimise her personal contribution to the costs
but ensures that her demand is satisfied.
\section{Matroids}
In this section we present the combinatorial structure of Matroids.
\todo{why matroids?}
